\documentclass[11pt,a4paper,sans]{moderncv}
\pdfoutput=1

\moderncvstyle{classic}
\moderncvcolor{grey} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.75]{geometry}
\usepackage{fontawesome}


\title{Curriculum Vitae}
\name{Andrew}{Hickman}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{124 Lenton Boulevard}{Nottingham}{NG7 2BZ}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{+44 7453 962930}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\email{andrew.hickman1@sky.com}
\homepage{github/andrewhickman}

\begin{document}

\makecvtitle

\section{Profile}
Third year student of Mathematics at Nottingham University. Hard-working and
efficient with experience working in a team environment and skilled at learning new technologies. Based in UK but willing to relocate.

\section{Education}
\cventry{2014--Present}{Nottingham University}{}{}{}{Working towards Mathematics BSc (Hons), expected First Class.}
\cventry{2007--2014}{Wallington County Grammar School}{}{}{}{\newline{}%
  \begin{itemize}%
  \item A-Levels Mathematics (A*), Further Mathematics (B), Physics (B) and Chemistry (C);
  \item GCSEs 11 Subjects A--C including Maths and English.
  \end{itemize}}

\section{Work Experience}

\cventry{Summer 2015}{Core Croydon}{}{}{}{Weekly volunteering in accounts department.\newline{}%
Responsibilities included:
  \begin{itemize}%
    \item{Dealing with the accounts of a small charity.}
    \item{Preparing paperwork for auditing.}
    \item{Working in a busy office environment.}
  \end{itemize}
}

\cventry{September 2015}{EVO Energy}{}{}{}{Project dealing with a batch of faulty components.\newline{}%
Responsibilities included:
  \begin{itemize}%
    \item{Maintaining a large spreadsheet.}
    \item{Manipulating large amounts of data.}
    \item{Tracking down a large number of customers and putting together a plan on how
    best to contact them.}
  \end{itemize}
}

\section{Technology Skills}
\cvlistitem{Proficient with Python and C++.}
\cvlistitem{Have also used technologies such as Matlab, HTML, LATEX, and Haskell}
\cvlistitem{Adept with both Windows and Linux.}
\cvlistitem{Experienced in Microsoft Office applications including Excel.}

\section{References}
\cvlistitem{References available on request.}


\end{document}
